### 2016-03-02 ch02-qlogms/excitation-design.tex
Add guideline boxes

>>>>

\begin{guideline}[Use quasi-logarithmic multisines as initial excitation.]
  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of many sharp resonance peaks over a wide frequency band of interest with a constant quality.
\end{guideline}

\begin{guideline}[Ensure $a$ ]
   To measure a resonant system with damping $\damping > \damping[\min]$ well, a (pink) quasi-logarithmic multisine with frequency ratio $\frac{\omega_k}{\omega_{k-1}} = \alpha \leq 1 + \damping[\min]$ is required.
\end{guideline}

\begin{guideline}[Ensure $\Delta \omega < (\damping - \damping^2) \wn \approx \damping \wn$]
 A quasi-logarithmic multisine with frequency resolution $\Delta \omega$ and tuned frequency spacing $\alpha = 1 + \damping$ allows to identify resonance peaks with $\wn$ well.
\end{guideline}
